Dynamical modeling of tidal streams

### 2013-12-28 tex/ms.tex
streams: illustration caption

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Carlberg(2009)]{Carlberg09a}
  Carlberg,~R.~G. 2009, \apj, 705, L223
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth,clip=]{track_aa.ps}\\
  \includegraphics[width=0.8\textwidth,clip=]{track_xz.ps}\\
  \includegraphics[width=0.8\textwidth,clip=]{track_ld.ps}
  \caption{}\label{fig:track}
%python illustrate_track.py ../tex/track_aa.ps ../tex/track_xz.ps ../tex/track_ld.ps
\end{figure}

>>>>

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Carlberg(2009)]{Carlberg09a}
  Carlberg,~R.~G. 2009, \apj, 705, L223
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85a}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}

@@

\begin{figure}
  \includegraphics[width=0.8\textwidth,clip=]{track_aa.ps}\\
  \includegraphics[width=0.8\textwidth,clip=]{track_xz.ps}\\
  \includegraphics[width=0.8\textwidth,clip=]{track_ld.ps}
  \caption{Illustration of the determination of the average stream
    track described in \sectionname~\ref{sec:track}. The small black
    dots in each panel are the points along the progenitor track at
    which the Jacobian $\partial (\veco,\veca) / \partial
    (\vecx,\vecv)$ is calculated. The large black dots are the
    coresponding points on the stream where the track is
    calculated. The dashed line in each panel is the progenitor's
    orbit, while the solid line and dash-dotted lines are the mean
    track and $2\sigma$ dispersion.}\label{fig:track}
%python illustrate_track.py ../tex/track_aa.ps ../tex/track_xz.ps ../tex/track_ld.ps
\end{figure}
